Project assignment - Tahoe-LAFS with SHA-3 candidates

### 2010-12-12 paper/main.tex
Comment
Added intro text to Introduction chapter

Thorough problem description. \\
Stepwise, what will we actually do?

Scope and objectives

@@

\input{tables/hashingtimes_1gb}
\input{tables/hashingtimes_100mb}
\input{tables/hashingtimes_1mb}
\input{tables/hashingtimes_1kb}
\input{tables/hashingtimes_1b}

@@

Four of the candidates has been shown to perform better than the currently used
SHA-256 -- BLAKE, BlueMidnightWish, Shabal and Simd. The time it takes for
Tahoe-LAFS to upload a one gigabyte file, could improve by $5\%$ if the best
performing SHA-3 candidate, BLAKE, were to be used.

Perhaps the most important finding in this project, is that the SUPERCOP
benchmarking indeed drives the development of new and better implementations
forward, but since the SUPERCOP \ac{API} does not conform to the \ac{NIST}
\ac{API}, the developers leave important functionality out (i.e.
{\verb update() }), and hence make it difficult for people who wish to try out
and test the \ac{SHA}-3 candidates in real world applications.

>>>>

The process of selecting what is to become the new standard for a secure hashing
algorithm is carried out by the {NIST}, and is at its final stages at the time
of writing. Fourteen candidates came through to the second round
\cite{s_nistround2}.

The Tahoe-\ac{LAFS} is a distributed, secure file system perfectly suited to
build file sharing services over the Internet. Currently it uses the
\ac{SHA}-256 algorithm to verify the integrity of files and shares, in addition
to creating keys, \ac{URI}s and more \cite{t_tahoe}.

In this project assignment, we integrate the fourteen \ac{SHA}-3 candidates in
the Tahoe-\ac{LAFS} and measure the performance impact. To be able to do this,
we create Python bindings for the best suited C implementations of the SHA-3
candidates, and alter the hash function calls in the source code of Tahoe.

@@

\input{tables/hashingtimes_1b}
\input{tables/hashingtimes_1kb}
\input{tables/hashingtimes_1mb}
\input{tables/hashingtimes_100mb}
\input{tables/hashingtimes_1gb}

@@

Four of the candidates has been shown to perform better than the currently used
SHA-256 -- BLAKE, BlueMidnightWish, Shabal and Simd. The time it takes for
Tahoe-LAFS to upload a one gigabyte file, could improve by $5\%$ if the best
performing SHA-3 candidate, BLAKE, were to be used.
% TODO: Bedre og bedre implementasjoner kommer til å komme for SHA-3
Perhaps the most important finding in this project, is that the SUPERCOP
benchmarking indeed drives the development of new and better implementations
forward, but since the SUPERCOP \ac{API} does not conform to the \ac{NIST}
\ac{API}, the developers leave important functionality out (i.e.
{\verb update() }), and hence make it difficult for people who wish to try out
and test the \ac{SHA}-3 candidates in real world applications.
